\setcounter{curtask}{10}

\mytitle{4 (на 14.02)}

\begin{task}
    Пусть $L$~--- счетный язык. Покажите, что для любого бесконечного кардинала
    $\alpha$ существует не более $2^{\alpha}$ неихоморфных $L$-структур мощности $\alpha$.
\end{task}

Назовем функцию $f:M^{n} \to M^{m}$ выразимой, есть ее график выразим.

\begin{task}
	Докажите, что:
    а) если $f, g$ выразимы, то $f(g)$ также выразима.
    б) если $f:M^{n} \to M$ выразима, то образ выразим.
    б) если $f:M^{n} \to M$ выразимая биекция, то $f^{-1}$ выразима.
\end{task}

\begin{task}
    Выразима ли константа $c$ в поле рациональных функций?
\end{task}

\breakline

\begin{ptask}{4}
    Let $T$ be the following theory in the language $\{<, R, B\}$, where $R$ (red) and $B$ (blue) are two unary predicate letters.
	$T$ consists of the axioms of DLO, together with 
	\[ \forall xy \exists zw (x<z<w<y \; \wedge \; R(z) \; \wedge \; B(w)) \]
	\[ \forall x \; (R(x)\; \vee \; B(x)) \]
	\[ \forall x \; (R(x) \leftrightarrow \neg B(x). \]
	Prove that $T$ is $\omega$-categorical (i.e. has a unique countable infinite model).
\end{ptask}

\begin{ptask}{8}
    \begin{itemize}
        \item Does the theory GROUPS prove the statement $\forall x\; y\;
        	(x\cdot y = y \cdot x)$?
        \item Is the statement $\forall xy\; \exists z\; (x<z \wedge z<y)$ provable
	    in LO?
    	\item Does ZF prove $\exists x \; \forall y\; (y\in x)$?
    	\item Does RCF prove ``every polynomial of degree 3 has a root''?
			(You are allowed to use completeness of RCF if necessary.)
		 \item Does RCF prove ``every polynomial of degree 2 has a root''? 
			 (You are allowed to use completeness of RCF if necessary.)
    \end{itemize}
\end{ptask}

\begin{ptask}{9}
  	Существует ли модель $RCF$, которая содержит $\mathbb{R}$ и такую точку $r$, что
    $r$ больше любого натурального числа $n$.
\end{ptask}