\section{Seminars}

\subsection{Seminar 1}

\begin{enumerate}
    \item Motivation. $AC_0[2]$-Frege, $\ResL$ proof system. (\cite{Kraj16}. Introduction).
    \item Communication protocols. Depth and size of communication protocols. Protocols and
        rectangles. (\cite{NK97}).
    \item $\KW$ and $\KW^m$ relations. Proof of Karchmer-Wigderson Theorem. (\cite{NK97} ch. 10).
    \item Canonical search problem ($\Search_{\varphi}$). Extraction of communication protocols for
        tree-like resolution and $\CP$. (\cite{PitNote14} lecture 7).
    \item Naive generalization to dag case. Problems with rectangles.
    \item Rectangles and ``valid'' vertices.
    \item Definition of boolean dag protocols. (\cite{Sok17} sec. 2).
    \item KW Theorem for protocols and problems in non-monotone case. (\cite{Sok17} sec. 3.2).
\end{enumerate}


\subsection{Seminar 2}

\begin{enumerate}
    \item Resolution proofs and dag protocols for $\Search_{\varphi}$. Problems with $\CP^*$.
    \item Dag games with bounded communication complexity (PLS games). (\cite{Sok17} sec. 3.1,
        \cite{Razb95} sec. 2.3 and 3).
    \item Reduction of inner communication complexity. KW Theorem in non-monotone case. $\CP^*$ proofs
        and dag protocols. (\cite{Sok17} sec. 3.1).
    \item Separation of resolution and dag protocols.
    \item Real dag protocols and $\CP$ proofs. (\cite{Sok17} sec. 4, \cite{HruPud17} sec. 3).
    \item $\EQ$ dag protocols.
    \item Hierarchy of protocols.
\end{enumerate}


\subsection{Seminar 3 (plan)}

\begin{enumerate}
    \item Monotone real circuits and real dag protocols. (\cite{HruPud17} sec. 3).
    \item Lower bound on real dag protocols via \textit{bottleneck technique}. \textit{Broken Mosquito
        Screen} formulas. (\cite{HakCook99}, \cite{Sok17}).
\end{enumerate}